Assessing Reliability of JavaScript Engines by Leveraging Diversity

### 2018-08-01 paper/paper.tex
pass on results

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Differential Testing Runtime Engines--Lessons Learned from the
  JavaScript Domain}

@@

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations (see
Section~\ref{sec:es6-design}). It is natural to expect that such
improvements will entail sensible changes in runtime
engines~\cite{kangax}; changes that could lead to errors. Even small
changes can have a large impact in practice. For example, in October
2014 a new attribute added to the Array datatype caused a bug that
resulted in MS Outlook web not working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. To
sum, finding bugs in JS engines is an important problem specially
because of the speed the specification evolves and the availability of
various public engines.

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find bugs
in
software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.
Cross-engine differential testing, in contrast, checks correctness by
comparing the output produced by \emph{different} engines on a given
input~\cite{patra2016learning}. Although different implementations of
JS engines today (see Table~\ref{tab:engines}), this technique is not
used in practice.

%% WHAT WE DID
This paper reports the results of a study we conducted to (i) assess
the reliability of existing JS engines and to (ii) evaluate the
importance of different factors when using DT. More precisely, we
analyzed the impact of two orthogonal factors in DT: test mining and
fuzzing. The first factor--\emph{test mining}--considers the effect
that \js{} test files mined from the repositories of open-source
engines have in detecting functional bugs in other engines. The second
factor--\emph{fuzzing}--considers the impact in bug detection of
fuzzing these files.
%% WHAT WE FOUND
To sum, we found that \Fix{...}

@@

\section{Infrastructure}
\label{sec:design}

@@

Figure~\ref{fig:workflow} illustrates the infrastructure we used in
this study.  The bug-finding process takes on input JS files from
regression test suites of various JS engines and generates warnings on
output. Boxes in the figure denote encapsulation; arrowed lines
indicate data flow. The cycle icons denote repetition--the leftmost
icon indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.
Considering the case where fuzzing is not selected, the oracle checks
whether or not the output produced for the input file is consistent
across all engine implementations. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. We used the open-source eshost-cli
project~\cite{eshost-cli} for that. Microsoft uses eshost-cli to check
functional discrepancies in the Chakra JS engine. Considering the case
where fuzzing~\cite{fuzz-testing-history} is selected, new inputs are
obtained from a given input using some off-the-shelf fuzzer. The
workflow with fuzzing is similar to the workflow without fuzzing. In
this case, however, the checker can produce multiple warnings for a
given input. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are
generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.

\Mar{explain what is a bucket (we refer to it later).}
The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases where the anomaly has
been detected in during the execution of test code or its close
%% the rationale we provide is related to the above; not crashes
neighborhood. The rationale is that the test in this group executed
without violating any internal checks of the API. In constrast,
warnings in the LO group reflect the cases where the anomaly was
observed during the execution of functions from standard JS libraries\Fix{check}.
  We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
%% \Igor{these cases happen because the specification describes how a function
%% should work, however the internal implementation is defined by the
%% engine developers}\Mar{If you confirm that there is no code in specs
%%   (see comment above), what would be those abstract
%%   functions/interfaces that you mentioned to me the other day?}.
In those cases, our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the fuzzed test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only \Fix{12\%} of the reals bugs
we found originated from the LO category.

% I think this will make the definition of HI/LO weaker. We can
% elaborate this later. for example, in the evaluation.
%% \Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
%% due the capacity of a fuzzer add an infinite repetition statement. We expected that
%% each test process can running utmost 5 seconds, if exceed this condition we stop 
%% the process and add a output message of a TIMEOUT error.}

% \Igor{
%   We defined if a warning is in HI or LO group according to console output.
%   The error stream in the output shows relevant informations that we can 
%   process. The Figure~\ref{fig:error-output} shows examples of HI and LO warning
%   outputs based on the stream output came from Chakra engine. 
  % The error message shows informations related to the assertion code (see at line 2) 
  % that thows an Error exception. This case was considered as HI groups and after 
  % several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
% }\Mar{igor, first add the real example then draft the discussion}

% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function, 
%     typeof, return, throw, new, Error, if},
%   }
% \begin{lstlisting}

% \end{lstlisting}
% \normalsize
% \caption{Warning captured as HI priority.}
% \label{fig:hi-priority}
% \end{figure}

% bug high console output
% This a case of a warning reported as HI priority, the Figure~\ref{} shows
% the output console of V8 engine. We consider this case as a HI group due 
% the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}

% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function, 
%     typeof, return, throw, new, Error, if},
%   }
% \begin{lstlisting}
% function test() {
%   var buffer = new ArrayBuffer(64);
%   var view = new DataView(buffer);
%   view.setInt8 (0, 0x80);
%   -return view.getInt8(0) === -0x80;

%   // radamsa fuzzing
%   +return view.getInt8(-1770523502845470856862803727694) === -0x80;
%   }

%   if (!test())
%       throw new Error("Test Failed");
% \end{lstlisting}
% \normalsize
% \caption{Warning captured as HI priority.}
% \label{fig:hi-priority}
% \end{figure}

% no-bug low console output
% \begin{figure}[h!]
%   \centering
%   \scriptsize
%   \lstset{escapeinside={@}{@},
%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%     numberstyle=\tiny,
%     morekeywords={assertEq, var, yield, in, function, 
%     typeof, return, throw, new, Error, if},
%   }
%   \begin{lstlisting}
% \end{lstlisting}
% \normalsize
% \caption{Warning captured as HI priority.}
% \label{fig:lo-priority}
% \end{figure}

%% \Mar{can we detect dups mining issue trackers?}
%% \Igor{
%%   acho que encontrar duplicatas seria um estudo a parte, devido a linguagem natural.
%%   Tenho umas consideracoes:
%%   \begin{itemize}
%%     \item warning HI possui a msg "Error: Test Failed", nao tem como buscar algo com isso, 
%%     se for pegar a linha que falhou, provavelmente vai mostrar a linha onde o assert se encontra.
%%     \item warning LO: podemos tentar conseguir buscar pelo output/funcao que falhou,
%%     \item O fuzzinator tem algo similar (dei uma olhada rapida, nao eh complicado)
%%   \end{itemize}
%% }\Mar{i think this is not the proper place to
%%   add this. discuss this with me.}

@@

We look for highly-maintained (as per the first criterion) and popular
(as per the second criterion) projects. As we wanted to report bugs,
we also looked for project with public issue trackers.
It is worth noting that we used
GoogleChromeLab's JSVU~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Group & Name & URL & \# Stars \\
    \midrule
    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
    Google & v8 & \cite{v82018repo} & 9800+ \\
    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    \midrule
    \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

We uses two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
\emph{existing} inputs randomly. The strenght of the approach is
limited by the supported mutation operators, which are typically
simple, and the quality of the test suite. We chose \radamsa\ and
\quickfuzz\ \Fix{...}

@@

The overarching goal of our study is to identify the ability of
cross-engine differential testing to find bugs in \js\ engines. We
organized our study in two parts. First, we investigated the stability
of the engines we analyzed. The intuition is that discovered bugs
would have low relevance if the engines are unstable. Then, we
analyzed the impact of using cross-engine differential testing to find
bugs in \js{} engines.

@@

We evaluated stability using different source of test cases. We used
the official \js{} conformance test suite and test suites developed
independently by each engine developing team. The Test262 suite is the
primary suite that we used to assess stability of engines. We ran this
suite once per day for seven consecutive days. Table~\ref{tab:test262}
shows results. To sum, we observed that \Fix{...}

@@

@@

\subsection{Differential Testing}

@@

%\bibliographystyle{IEEEtran}
\bibliographystyle{plain}
\bibliography{references,../docs/google-research-awards-latam/tmp}

>>>>

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Assessing Reliability of JavaScript Engines by Leveraging Diversity}

@@

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations. It is natural to expect that
such improvements entails sensible changes in runtime engines. Even
small changes can have a large impact in practice. For example, in
October 2014 a new attribute added to Array objects caused a bug that
resulted in MS Outlook web not working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. To
sum, finding bugs in JS engines is an important problem specially
because of the speed the specification evolves and the availability of
various public engines today~\cite{kangax}.

%% WHAT WE DID
This paper reports the results of a study we conducted to assess
reliability of existing JS engines by leveraging implementation
diversity in two orthogonal ways. The first method considered is
\emph{test transplantation}. This approach evaluates the effects that
running \js{} test files from a given engine have in detecting bugs in
other engines. The intuition is that when bugs are found in some
engine implementation a test case is created and added to the
regression suite. Those test inputs often check interesting corner
cases that could reveal bugs in different engine implementations. The
second method considered is \emph{cross-engine differential
  testing}. This method fuzzes existing inputs, using existing
techniques, and then compares the output produced by different engines
using a differential oracle. One possible cause of output discrepancy
is a bug. It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find bugs in
software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks correctness by comparing the output produced by
\emph{different engines} on a fuzzed
input~\cite{patra2016learning}. This approach is not popularized,
certainly because it is more challenging to fully automate--a number
of legitimate reasons exist, other than a bug, for a test execution to
manifest discrepancy (see Table~\ref{tab:false-positives}).

%% WHAT WE FOUND
To sum, we found that \Fix{...}

@@

\section{Differential Testing Infrastructure}
\label{sec:design}

@@

Figure~\ref{fig:workflow} illustrates the infrastructure we used for
differential testing.  The bug-finding process takes on input JS files
from regression test suites of various JS engines and generates
warnings on output. Boxes in the figure denote encapsulation; arrowed
lines indicate data flow. The cycle icons denote repetition--the
leftmost icon indicates that each file in the input list will be
analyzed in separate whereas the rightmost icon shows that a single
file will be fuzzed multiple times. The bug-finding process works as
follows.

New inputs are obtained for a given test input using some
off-the-shelf input fuzzer~\cite{fuzz-testing-history}.\Comment{
  Several fuzzing methods have been proposed in the past, varying with
  respect to how new inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. Note that a number of reasons exist, other than a bug, to
explain discrepancy (see Table~\ref{tab:false-positives}). We used the
open-source eshost-cli project~\cite{eshost-cli} for checking output
discrepancy. Microsoft uses that tool in the Chakra JS engine.

%The checker can produce multiple warnings for a given input.

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we classified warnings in two
kinds, reflecting their likelihood to manifest a real bug. Warnings of
the kind ``\hi{}'' are associated with the cases where the anomaly has
been detected in the execution of the test code or its harness. The
rationale is that the test in this group executed without violating
any internal checks of the API. In constrast, warnings in the
``\lo{}'' group reflect the cases where the anomaly was observed
during the execution of functions not related to the test itself. We
found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another and that is
acceptable.  In those cases, our infrastructure would observe a
discrepancy that is more likely to be associated with an invalid input
produced by the fuzzer, \ie{}, a bug in the test not the
code. Although we did find real bugs from ``\lo{}'' warnings, the
proportion was much lower compared to the ``\hi{}'' warnings. Overall,
only \Fix{12\%} of the reals bugs we found originated from ``\lo{}''
warnings.

\Mar{explain what is a bucket (we refer to it later).}

@@

We look for highly-maintained (as per the first criterion) and popular
(as per the second criterion) projects. As we wanted to report bugs,
we also looked for project with public issue
trackers. Table~\ref{tab:engines} lists the engines we analyzed in
this work. It is worth noting that we used GoogleChromeLab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Team & Name & URL & \# Stars \\
    \midrule
    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
    Google & v8 & \cite{v82018repo} & 9800+ \\
%    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    %% \midrule
    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    Mozilla & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
\emph{existing} inputs randomly. The strenght of the approach is
limited by the supported mutation operators, which are typically
simple, and the quality of the test suite. We chose \radamsa\ and
\quickfuzz\ \Fix{...elaborate...}

@@

Recall that the goal of our study is to assess reliability of
\js\ engines by leveraging the rich diversity of implementations in
this domain. We report results in three parts. First, we report on the
stability of the engines we analyzed using the EcmaScript standard
conformance test suite Test262~\cite{ecma262-conformance-suite}. The
intuition is that the bugs we discover would have low relevance if the
engines are unstable (\ie{}, too fragile). Second, we report results
obtained with test transplantation. The hypothesis is that test cases
written for one engine may reveal bugs in different engines. The
rationale is that the domain of possible inputs is just too large;
consequently, test suites of a given engine will cover scenarios and
corner cases uncovered by another engine.  Third, we analyzed the
impact of using cross-engine differential testing to find bugs in
\js{} engines. \Fix{hypothesis/rationale}

@@

We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once per day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that some engines, namely \smonkey{}, \Fix{...}, have
variants of Test262 as part of their regression test suite\Mar{with
  fewer tests?}. We used the official version instead. To sum, we
observed that \Fix{...} \Mar{check connection with kangax report}

@@

\subsection{Test Transplantation}

@@

\subsection{Cross-Engine Differential Testing}

@@

%\bibliographystyle{IEEEtran}
\balance
\bibliographystyle{plain}
\bibliography{references,../docs/google-research-awards-latam/tmp}
